\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-12 main.Rmd
added acknowledgements section

>>>>

# Acknowledgements {-}

We would like to thank Stuart Lee and Heike Hofmann for their feedback about this work. The most recent version of the `frame_calendar` function is included in the **sugrrants** package, which can be accessed via the CRAN website <https://CRAN.R-project.org/package=sugrrants> or Github <https://github.com/earowang/sugrrants>. All materials required to reproduce this article and a history of the changes can be found at the project's Github repository <https://github.com/earowang/paper-calendar-vis>.

### 2018-10-12 main.tex
added acknowledgements section

>>>>

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

We would like to thank Stuart Lee and Heike Hofmann for their feedback
about this work. The most recent version of the \texttt{frame\_calendar}
function is included in the \textbf{sugrrants} package, which can be
accessed via the CRAN website
\url{https://CRAN.R-project.org/package=sugrrants} or Github
\url{https://github.com/earowang/sugrrants}. All materials required to
reproduce this article and a history of the changes can be found at the
project's Github repository
\url{https://github.com/earowang/paper-calendar-vis}.
